### 2019-10-25 paper/results.tex
After Tikhomirov's and Matthew's comments

The thorium feed mechanism adopts continuous feed flow of external thorium (from Th stockpile) and 
$^{233}$U from \texttt{Pa-decay tank}. The molar fraction of the heavy metal 
in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
Additionally, the initial fissile material fraction was increased for the five fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the Beginning Of Life (BOL). 
Figure~\ref{fig:keff1} illustrates the effective multiplication factor 
dynamics during reactor operation for the thorium feed mechanism. As shown in 
Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) 
decreases sharply during the first 25 years of reactor operation for the first 
four cases. $k_{eff}$ decreases as a result of depletion of the initial 
fissile materials and production of poisonous fission products. Thus, the 
reactor becomes subcritical relatively quickly for alternative startup 
compositions ($\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
years in the Pu reactor-grade case). The amount of $^{233}$U generated in 
the \gls{SD-TMSR} is not enough to maintain the reactor criticality and 
counteract parasitic neutron absorption. Nevertheless, 
the continuous feed flow of thorium and $^{233}$U helps to operate the 
\gls{SD-TMSR} for a lifetime-long period of time (Figure~\ref{fig:keff1} (U-233 case)). 
Additionally, the molar fraction of the LEU and Pu reactor-grade in the initial fuel composition was increased
more, consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (LEU and Pu reactor-grade cases)). Nevertheless, $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.

@@

The non-thorium feed mechanism allows continuous feed flow of 
$^{233}$U from \texttt{Pa-decay tank} and external Heavy Metal (excluding Th). 
Under the non-thorium feed mechanism, four different initial fissile materials were studied: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, and \gls{TRU}. The continuous feed of $^{233}$U 
without $^{232}$Th will lead to supercritical reactor, thus the $^{233}$U case 
is excluded from non-thorium feed mechanism study.
The molar fraction of the heavy metal in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
Additionally, the initial fissile material fraction was increased for the four fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the Beginning Of Life (BOL). 
Figure~\ref{fig:keff2} shows the change of the effective multiplication factor 
during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism. Both Pu reactor-grade and TRU case 
show promising results relative to the other two cases (LEU and Pu+LEU) (see Figure~\ref{fig:keff2}). 
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff2.png}
			\vspace{-0.5in}
	\caption{The change of the effective multiplication factor during 60 
	\gls{EFPY} of reactor operation for non-thorium feed mechanism (confidence 
	interval $\pm\sigma$ is shaded).} 
	\label{fig:keff2}
\end{figure}

For the Pu reactor-grade case, the amount of $^{233}$U generated in the \gls{SD-TMSR} in addition to the external feed flow of Pu is sufficient to maintain the reactor criticality and counteract the neutron absorption in the initial non-fissile isotopes and FPs. 
For the \gls{TRU} fuel salt, the amount of 
$^{233}$U and the external feed flow of TRU is barely enough to operate the 
reactor for a long period of time ($\approx$ $40$ years) without any 
external feed of $^{233}$U ($^{233}$U used only from \texttt{Pa-decay tank}). Nevertheless, $k_{eff}$ decreases with the burnup 
because the \glspl{MA}\footnote{In the present work, the Minor Actinides 
(MA) include Np, Am and Cm.} accumulating in the core as a result of 
continuous TRU feed. As shown in Figure~\ref{fig:keff2}, the LEU and Pu+LEU 
fuel are less attractive for non-thorium feed mechanism. The continuous LEU 
feed increases the amount of fertile $^{238}$U and consequently, reduces the 
feasibility of such fissile materials. According to the $k_{eff}$ 
results, Pu reactor-grade and TRU are only alternative fissile materials that  
can be used to startup and maintain operation of the \gls{SD-TMSR}.

\subsection{Pu reactor-grade, TRU, and $^{233}$U initial fuel}
In this section, the simulation of the SD-TMSR with Pu reactor-grade and TRU 
fissile materials is discussed. Additionally, previously studied the $^{233}$U 
case is listed for comparison \cite{ashraf2019whole_core}. 
Figure~\ref{fig:refillCCC} demonstrates the dynamics of heavy metal refill 
rate during 60 \gls{EFPY} of the SD-TMSR operation. The heavy metal refill 
rate was adjusted to maintain the reactor critical and the total fuel mass 
almost constant\footnote{The variation of the total fuel mass is less than 
$0.1\%$} during the reactor operation. In the $^{233}$U case, the mean values of 
$^{233}$U and $^{232}$Th refill rate are $1.77$ and $2.21$ $kg/d$, 
respectively. Similarly, in the Pu reactor-grade case, the mean values of 
$^{233}$U and Pu refill rate are $0.75$ and $2.75$ $kg/d$, respectively. For  
the TRU case, the mean values of $^{233}$U and TRU refill rate are $0.90$ and 
$2.0$ $kg/d$, respectively.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{refillCCC.png}
			\vspace{-0.5in}
	\caption{Dynamics of heavy metal refill rate during 60 \gls{EFPY} of 
		reactor operation. Solid lines for $^{233}$U case, dashed lines for Pu 
		reactor-grade case, and dotted lines for TRU case.}
	\label{fig:refillCCC}
\end{figure}

Figure~\ref{fig:inventoryCCCC} and ~\ref{fig:inventoryPu_TRUCCC} demonstrate 
the evolution of important isotopes for $^{233}$U, Pu and TRU cases 
respectively. For the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}), the mass of Pa in the fuel salt is almost constant and reaches 
$17.8$  $kg$ at the end of the operation time. 
Additionally, the mass of Minor Actinides (MA) and Pu increases with time. The level of Pu in the fuel salt correlates with the mass of the MA. Moreover, MA needs more time to reach equilibrium than Pu. Uranium inventory increases during 
operation and reaches equilibrium after $\approx$ $27$ years. Figure~\ref{fig:inventoryCCCC} shows that refueling the core with Th helps 
maintain an almost constant inventory throughout the full operation time. 
For Pu and TRU cases (Figure~\ref{fig:inventoryPu_TRUCCC}), the protactinium extraction time was selected equal 30s 
to avoid poisoning the core. Therefore, 
Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel salt 
is relatively low when compared to Pa mass in the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}). Major 
isotopes for all three cases reach the equilibrium state after $\approx$ $30$ 
years (see Figure~\ref{fig:inventoryCCCC} and ~\ref{fig:inventoryPu_TRUCCC}).
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{inventoryCCCC.png}
	\vspace{-0.4in}
	\caption{Evolution of the important nuclides inventories for $^{233}$U 
		case (MA involves Np, Am, Cm) \cite{ashraf2019whole_core}.}
	\label{fig:inventoryCCCC}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{inventoryPu_TRUCCC.png}
	\vspace{-0.5in}
	\caption{Evolution of the important nuclides inventories for Pu 
		reactor-grade case (solid lines) and for TRU case (dashed lines).}
	\label{fig:inventoryPu_TRUCCC}
\end{figure}

Figure~\ref{fig:Th232CC} illustrates the variation of thorium inventory in the 
fuel salt for $^{233}$U, Pu reactor-grade and TRU cases. The thorium inventory 
decreases in the $^{233}$U case by only $3.2$\% at the End Of Life (EOL) when the thorium 
feed mechanism was applied. 
In contrast, thorium total mass decreases significantly in Pu and TRU cases when the non-thorium 
feed mechanism was applied. Thus, thorium mass decreases by $39.2$\% and 
$37.96$\% for Pu reactor-grade and TRU cases, respectively.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Th232CC.png}
	\caption{The variation of thorium mass in the fuel salt for $^{233}$U, Pu reactor-grade, and TRU cases.}
	\label{fig:Th232CC}
\end{figure}

Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt 
for $^{233}$U, Pu reactor-grade and TRU cases. Notably, the mass of the 
$^{233}$U reaches the equilibrium after $\approx$ $30$ years. Overall, the 
amount of $^{233}$U is sufficient to maintain criticality in 
the three cases.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{U233CC.png}
	\caption{Mass of $^{233}$U in the fuel salt for $^{233}$U, Pu reactor-grade, and TRU cases.}
	\label{fig:U233CC}
\end{figure}

In the non-thorium feed mechanism, the SD-TMSR is continuously refueled by HM (Pu and TRU) for 
criticality, which increases the Pu molar fraction (mole\%) in the molten salt. 
According to the literature, the limit of Pu solubility in the FLiBe salt is 
$\approx$ $4.0$ mole\% \cite{ignatiev2012progress,sood1975plutonium}. 
Figure~\ref{fig:PusolubilityCC} represents the Pu fraction in the fuel salt 
(mole\%) for $^{233}$U, Pu reactor-grade and TRU cases, respectively. In $^{233}$U and Pu reactor-grade cases, the Pu fraction increases 
slightly but still below its solubility limit. On the other hand, the Pu 
fraction in the molten salt loaded by TRU increases during operation and 
reaches the Pu solubility limit after $\approx$ $40$ years. This issue may 
be solved by increasing the reactor operation temperature or reducing the 
HM initial inventory \cite{zou2018transition}.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{PusolubilityCC.png}
	\caption{The Pu fraction in the fuel salt (mole\%) for $^{233}$U, Pu reactor-grade, and TRU cases.}
	\label{fig:PusolubilityCC}
\end{figure}
\FloatBarrier

Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U during 
operation for $^{233}$U, Pu reactor-grade and TRU cases, respectively. For the TRU case, the net production of $^{233}$U is almost 
zero. 
Although all produced $^{233}$U was used to refuel the core, the reactor was subcritical after $40$ years of operation (Figure~\ref{fig:keff2}).
In $^{233}$U and Pu reactor-grade cases, the net production of 
$^{233}$U increases with burnup and reaches at the end of operation lifetime 
about $1.77$ $t$ and $10$ $t$, respectively. As shown in 
Figure~\ref{fig:NetCC}, for the $^{233}$U case, after 26 years the net production of $^{233}$U reaches 
$1.3$ $t$; this is sufficient to startup another \gls{SD-TMSR}. Similarly, 
one can see that the same amount of $^{233}$U ($1.3$ $t$) can be achieved 
after $\approx$ $4.5$ years if we applied the non-thorium feed mechanism on 
the SD-TMSR that initially loaded by Pu reactor-grade alternative to 
$^{233}$U. In addition, Figure~\ref{fig:NetCC} also shows that for $^{233}$U 
case the net production of $^{233}$U during the first 455 days is negative, 
thus about $175.28$ $kg$ of $^{233}$U must be added during this period. 
In conclusion, the thorium fuel cycle transition can be achieved by selecting the 
proper feed mechanism and initial fissile material. 
Specifically, applied non-thorium feed mechanism on 
the SD-TMSR loaded by Pu reactor-grade allows the 
transition to the thorium fuel cycle after $\approx$ 
$4.5$ years. Additionally, applied thorium feed mechanism on 
the SD-TMSR loaded by $^{233}$U allows the 
transition to the thorium fuel cycle after $26$ years of operation. 
The comparison between the two feed mechanisms with different types of initial 
fuel is listed in Table~\ref{tab:comp_feeds}.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{NetCC.png}
	\caption{Net production of $^{233}$U during burnup period (60 \gls{EFPY}) for $^{233}$U, Pu reactor-grade, and TRU cases.}
	\label{fig:NetCC}
\end{figure}

\begin{table}  [!h]
	\begin{minipage}{\linewidth}
		\renewcommand\footnoterule{}
		\renewcommand{\thefootnote}{\alph{footnote}}
		\caption{Comparison between the two feed mechanisms for the five different 
			types of initial fuel.}
		\label{tab:comp_feeds}
		\vspace{0.1in}
		\begin{tabularx}{\textwidth}{p{0.22\textwidth} X p{0.18\textwidth} 
				p{0.14\textwidth} X X 
			}  %{\textwidth}
			\hline
			Feed mechanism & \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) & Pu 
			reactor-grade & \gls{TRU}& $^{233}$U \\
			\hline
			Thorium feed\\ mechanism&\xmark&\xmark&\xmark&\xmark& \cmark \\
			Non-thorium feed\\ mechanism &\xmark&\xmark&\cmark\footnotemark[1] 
			&\cmark\footnotemark[2] & \xmark\footnotemark[3] \\
			\hline
		\end{tabularx}
		\vspace{-1.5ex}%
		\footnotetext[1]{Positive $^{233}$U net production and critical 
			configuration for 60 years of operation.}
		\footnotetext[2]{Zero $^{233}$U net production and critical 
			configuration for 40 years of operation.}		
		\footnotetext[3]{Too large and increasing $k_{eff}$ during 
			lifetime.}		
	\end{minipage}
\end{table}
\FloatBarrier

\subsection{Neutron spectrum}
Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
lethargy for full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 
MeV for the $^{233}$U, Pu reactor-grade, and TRU cases at BOL and EOL. In $^{233}$U 
case, at the EOL, the neutron spectrum is harder than at BOL due to the 
accumulation of the Pu and other strong thermal neutron absorbers in the fuel 
salt. For Pu reactor-grade and TRU cases, during the reactor operation, the 
fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
(see Figure~\ref{fig:U233CC}), the neutron spectrum softens and becomes 
similar to a initial thermal spectrum of $^{233}$U fueled \gls{SD-TMSR}.
 \begin{figure}
 	\centering
 	\includegraphics[width=1.01\textwidth]{spectrumFLUX110vC.png}
 			\vspace{-0.4in}
 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for $^{233}$U, Pu reactor-grade, and TRU cases.}
 	\label{fig:spectrumFLUX110vC}
\end{figure}

@@

When the fuel salt temperature increases, the density of the salt decreases, 
but at the same time, the total volume of fuel salt in the 
core remains constant because it
is bounded by the vessel. When the graphite 
temperature increases, the density of
graphite decreases, creating additional 
space for the salt. The cross-section temperatures for the fuel and moderator 
were changed from 900 to 1000 K to determine the temperature coefficients. 
This work considered five different cases:
\begin{enumerate}
	\item Fuel salt temperature (Doppler Effect) rising from 900 to 1000 K 
	(first row  in Table ~\ref{tab:tcoe}).
	\item Fuel salt density decreasing from 3.3 to 3.233 g/cm$^3$ 
	(density change caused by temperature increase from	900 to 1000 K).
	\item Total fuel salt temperature (Doppler+density) rising from 900 to 
	1000 K.	
	\item Graphite temperature (Doppler Effect) rising from 900 to 1000 K.
	\item Whole reactor temperature rising from 900 K to 1000 K.
\end{enumerate}

>>>>

The thorium feed mechanism adopts continuous feed flow of external thorium from the thorium stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}. The molar fraction of the heavy metal 
in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
Additionally, the initial fissile material fraction was increased for the five fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the Beginning Of Life (BOL). 
Figure~\ref{fig:keff1} illustrates the effective multiplication factor 
dynamics during reactor operation for the thorium feed mechanism. As shown in 
Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) 
decreases sharply during the first 25 \gls{EFPY} of reactor operation for the first 
four cases. $k_{eff}$ decreases as a result of depletion of the initial 
fissile materials and production of poisonous fission products \gls{FPs}. Thus, the 
reactor becomes subcritical relatively quickly for alternative startup 
compositions, for example, $\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
years in the reactor-grade Pu case. The amount of $^{233}$U generated in 
the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) is not enough to maintain the reactor criticality and 
counteract parasitic neutron absorption. Nevertheless, 
the continuous feed flow of thorium and $^{233}$U helps to operate the 
\gls{SD-TMSR} for a lifetime-long period of time (Figure~\ref{fig:keff1} (U-233 case)). 
Additionally, the molar fraction of the LEU and reactor-grade Pu in the initial fuel composition was increased
more, consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (LEU and reactor-grade Pu cases)). Nevertheless, $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.

@@

The non-thorium feed mechanism allows continuous feed flow of 
$^{233}$U from the \texttt{Pa-decay tank} and external heavy metals (excluding Th). 
Under the non-thorium feed mechanism, four different initial fissile materials are studied: \gls{LEU}, Pu mixed with \gls{LEU}, reactor-grade Pu, and \gls{TRU}. The continuous feed of $^{233}$U 
without $^{232}$Th will lead to a supercritical reactor, thus the $^{233}$U case 
is excluded from the non-thorium feed mechanism study.
The molar fraction of the heavy metal in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
Additionally, the initial fissile material fraction was increased for the four fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the BOL. 
Figure~\ref{fig:keff2} shows the change of the effective multiplication factor 
during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism. Both the reactor-grade Pu and TRU cases 
show promising results relative to the other two cases (LEU and Pu+LEU) (see Figure~\ref{fig:keff2}). 
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff2.png}
			\vspace{-0.5in}
	\caption{The change of the effective multiplication factor during 60 
	\gls{EFPY} of reactor operation for non-thorium feed mechanism (confidence 
	interval $\pm\sigma$ is shaded).} 
	\label{fig:keff2}
\end{figure}

For the reactor-grade Pu case, the amount of $^{233}$U generated in the \gls{SD-TMSR}, in addition to the external feed flow of Pu, is sufficient to maintain the reactor criticality and counteract the neutron absorption in the initial non-fissile isotopes and FPs. 
For the \gls{TRU} fuel salt, the amount of 
$^{233}$U and the external feed flow of TRU is barely enough to operate the 
reactor for a long period of time ($\approx$ $40$ years) without any 
external feed of $^{233}$U ($^{233}$U used only from the \texttt{Pa-decay tank}). Nevertheless, $k_{eff}$ decreases with the burnup 
because of the \glspl{MA}\footnote{In the present work, the minor actinides 
(MA) include Np, Am, and Cm.} accumulating in the core as a result of 
continuous TRU feed. As shown in Figure~\ref{fig:keff2}, the LEU and Pu+LEU 
fuel are less attractive for the non-thorium feed mechanism. The continuous LEU 
feed increases the amount of fertile $^{238}$U and consequently, reduces the 
feasibility of such fissile materials. According to the $k_{eff}$ 
results, reactor-grade Pu and TRU are the only alternative fissile materials that  
can be used to startup and maintain operation of the \gls{SD-TMSR}.

\subsection{Reactor-grade Pu, TRU, and $^{233}$U initial fuel}
In this section, the simulation of the SD-TMSR with reactor-grade Pu and TRU 
fissile materials is discussed. Additionally, the previously studied $^{233}$U 
case is listed for comparison \cite{ashraf2019whole_core}. 
Figure~\ref{fig:refillCCC} demonstrates the dynamics of the heavy metal refill 
rate during 60 \gls{EFPY} of the SD-TMSR operation. The heavy metal refill 
rate was adjusted to maintain criticality and the total fuel mass 
almost constant\footnote{The variation of the total fuel mass is less than 
$0.1\%$} during reactor operation. In the $^{233}$U case, the mean values of 
$^{233}$U and $^{232}$Th refill rate are $1.77$ and $2.21$ $kg/d$, 
respectively. Similarly, in the reactor-grade Pu case, the mean values of 
$^{233}$U and Pu refill rate are $0.75$ and $2.75$ $kg/d$, respectively. For  
the TRU case, the mean values of $^{233}$U and TRU refill rate are $0.90$ and 
$2.0$ $kg/d$, respectively.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{refillCCC.png}
			\vspace{-0.5in}
	\caption{Dynamics of heavy metal refill rate during 60 \gls{EFPY} of 
		reactor operation. Solid lines for the $^{233}$U case, dashed lines for the
		reactor-grade Pu case, and dotted lines for the TRU case.}
	\label{fig:refillCCC}
\end{figure}

Figures~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC} demonstrate 
the evolution of important isotopes for the $^{233}$U, Pu, and TRU cases 
respectively. For the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}), the mass of Pa in the fuel salt is almost constant and reaches 
$17.8$  $kg$ at the end of the operation time. 
Additionally, the mass of minor actinides (MA) and Pu increases with time. The level of Pu in the fuel salt correlates with the mass of the MA; however, MA need more time to reach equilibrium than Pu. Uranium inventory increases during 
operation and reaches equilibrium after $\approx$ $27$ years. Figure~\ref{fig:inventoryCCCC} shows that refueling the core with thorium helps 
maintain an almost constant inventory throughout the full operation time. 
For the Pu and TRU cases (Figure~\ref{fig:inventoryPu_TRUCCC}), the Pa extraction time was selected to be 30 s 
to avoid poisoning the core. Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel salt 
is relatively low when compared to Pa mass in the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}). Major 
isotopes for all three cases reach the equilibrium state after $\approx$ $30$ 
years (see Figure~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC}).
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{inventoryCCCC.png}
	\vspace{-0.4in}
	\caption{Evolution of the important nuclides inventories for the $^{233}$U 
		case (MA involves Np, Am, Cm) \cite{ashraf2019whole_core}.}
	\label{fig:inventoryCCCC}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{inventoryPu_TRUCCC.png}
	\vspace{-0.5in}
	\caption{Evolution of the important nuclides inventories for the 
		reactor-grade Pu case (solid lines) and for the TRU case (dashed lines).}
	\label{fig:inventoryPu_TRUCCC}
\end{figure}

Figure~\ref{fig:Th232CC} illustrates the variation of thorium inventory in the 
fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases. The thorium inventory 
decreases in the $^{233}$U case by only $3.2$\% at the End Of Life (EOL) when the thorium 
feed mechanism is applied. 
In contrast, thorium total mass decreases significantly in the Pu and TRU cases when the non-thorium 
feed mechanism is applied. Thus, thorium mass decreases by $39.21$\% and 
$37.96$\% for the reactor-grade Pu and TRU cases, respectively.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Th232CC.png}
	\caption{The variation of thorium mass in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:Th232CC}
\end{figure}

Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt 
for the $^{233}$U, reactor-grade Pu, and TRU cases. The mass of 
$^{233}$U reaches equilibrium after $\approx$ $30$ years; overall, the 
amount of $^{233}$U is sufficient to maintain criticality in 
the three cases.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{U233CC.png}
	\caption{Mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:U233CC}
\end{figure}

In the non-thorium feed mechanism, the SD-TMSR is continuously refueled by heavy metals (Pu and TRU) for 
criticality, which increases the Pu molar fraction (mole\%) in the molten salt. 
According to literature, the limit of Pu solubility in the FLiBe salt is 
$\approx$ $4.0$ mole\% \cite{ignatiev2012progress,sood1975plutonium}. 
Figure~\ref{fig:PusolubilityCC} represents the Pu fraction in the fuel salt 
(mole\%) for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. In the $^{233}$U and reactor-grade Pu cases, the Pu fraction increases 
slightly but still below its solubility limit. On the other hand, the Pu 
fraction in the molten salt loaded by TRU increases during operation and 
reaches the Pu solubility limit after $\approx$ $40$ years. This issue may 
be solved by increasing the reactor operation temperature or reducing the 
HM initial inventory \cite{zou2018transition}.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{PusolubilityCC.png}
	\caption{The Pu fraction in the fuel salt (mole\%) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:PusolubilityCC}
\end{figure}
\FloatBarrier

Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U during 
operation for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. For the TRU case, the net production of $^{233}$U is almost 
zero. 
Although all produced $^{233}$U is used to refuel the core, the reactor is subcritical after $40$ years of operation (Figure~\ref{fig:keff2}).
In the $^{233}$U and reactor-grade Pu cases, the net production of 
$^{233}$U increases with burnup and reaches about $1.77$ $t$ and $10$ $t$ at EOL, respectively. As shown in 
Figure~\ref{fig:NetCC}, for the $^{233}$U case, after 26 years the net production of $^{233}$U reaches 
$1.3$ $t$; this is sufficient to start up another \gls{SD-TMSR}. Similarly, 
one can see that the same amount of $^{233}$U ($1.3$ $t$) can be achieved 
after $\approx$ $4.5$ years if we apply the non-thorium feed mechanism on 
the SD-TMSR that was initially loaded by reactor-grade Pu alternative to 
$^{233}$U. In addition, Figure~\ref{fig:NetCC} shows that for the $^{233}$U 
case the net production of $^{233}$U during the first 455 days is negative; 
about $175.28$ $kg$ of $^{233}$U must be added during this period. 
In conclusion, the thorium fuel cycle transition can be achieved by selecting the 
proper feed mechanism and initial fissile material. 
Specifically, applying the non-thorium feed mechanism on 
the SD-TMSR loaded by reactor-grade Pu allows the 
transition to the thorium fuel cycle after $\approx$ 
$4.5$ years. Additionally, applying the thorium feed mechanism on 
the SD-TMSR loaded by $^{233}$U allows the 
transition to the thorium fuel cycle after $\approx$ $26$ years of operation. 
The comparison between the two feed mechanisms with different types of initial 
fuel is listed in Table~\ref{tab:comp_feeds}.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{NetCC.png}
	\caption{Net production of $^{233}$U during the burnup period (60 \gls{EFPY}) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:NetCC}
\end{figure}

\begin{table}  [!h]
	\begin{minipage}{\linewidth}
		\renewcommand\footnoterule{}
		\renewcommand{\thefootnote}{\alph{footnote}}
		\caption{Comparison between the two feed mechanisms for the five different 
			types of initial fuel.}
		\label{tab:comp_feeds}
		\vspace{0.1in}
		\begin{tabularx}{\textwidth}{p{0.22\textwidth} X p{0.18\textwidth} 
				p{0.14\textwidth} X X 
			}  %{\textwidth}
			\hline
			Feed mechanism & \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) &  
			reactor-grade Pu & \gls{TRU}& $^{233}$U \\
			\hline
			Thorium feed\\ mechanism&\xmark&\xmark&\xmark&\xmark& \cmark \\
			Non-thorium feed\\ mechanism &\xmark&\xmark&\cmark\footnotemark[1] 
			&\cmark\footnotemark[2] & \xmark\footnotemark[3] \\
			\hline
		\end{tabularx}
		\vspace{-1.5ex}%
		\footnotetext[1]{Positive $^{233}$U net production and critical 
			configuration for 60 years of operation.}
		\footnotetext[2]{Zero $^{233}$U net production and critical 
			configuration for 40 years of operation.}		
		\footnotetext[3]{Too large and increasing $k_{eff}$ during 
			lifetime.}		
	\end{minipage}
\end{table}
\FloatBarrier

\subsection{Neutron spectrum}
Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
lethargy for a full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 
MeV for the $^{233}$U, reactor-grade Pu, and TRU cases at BOL and EOL. In the $^{233}$U 
case, at the EOL, the neutron spectrum is harder than at BOL due to the 
accumulation of Pu and other strong thermal neutron absorbers in the fuel 
salt. For the reactor-grade Pu and TRU cases, during reactor operation, the 
fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
(see Figure~\ref{fig:U233CC}); the neutron spectrum softens and becomes 
similar to the initial thermal spectrum of a $^{233}$U fueled \gls{SD-TMSR}.
 \begin{figure}
 	\centering
 	\includegraphics[width=1.01\textwidth]{spectrumFLUX110vC.png}
 			\vspace{-0.4in}
 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
 	\label{fig:spectrumFLUX110vC}
\end{figure}

@@

When the fuel salt temperature increases, the density of the salt decreases, 
but at the same time, the total volume of fuel salt in the 
core remains constant because it
is bounded by the vessel. When the graphite 
temperature increases, the density of
graphite decreases, creating additional 
space for the salt. The cross-section temperatures for the fuel and moderator 
were changed from 900 to 1000 K to determine the temperature coefficients. 
This work considered five different cases:
\begin{enumerate}
	\item Fuel salt temperature (Doppler Effect) rising from 900 to 1000 K 
	(first row  in Table~\ref{tab:tcoe}).
	\item Fuel salt density decreasing from 3.3 to 3.233 g/cm$^3$ 
	(density change caused by temperature increase from	900 to 1000 K).
	\item Total fuel salt temperature (Doppler+density) rising from 900 to 
	1000 K.	
	\item Graphite temperature (Doppler Effect) rising from 900 to 1000 K.
	\item Whole reactor temperature rising from 900 K to 1000 K.
\end{enumerate}
